### 2012-10-29 paper_draft.tex
Changed my name slightly (because PB is all over pubmed, PEB is not.). Added dotchart, linked to in text.

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp Bayer$^{2}$, 
Helge Rausch$^{3}$,
Fabian Zimmer$^{4}$,
Julia Reda$^{5}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} Applied Bioinformatics Group, School of Agriculture and Food Sciences, The University of Queensland, Australia
\\
\bf{3} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{4} Evolutionary Genomics and Transcriptomics Lab, Department of Genetics, Evolution and Environment, University College London, England
\\
\bf{5} Johannes Gutenberg University Mayence, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

\begin{figure}[!ht]
	\begin{center}

	\end{center}
	\caption{
	{\bf Flow of data inside openSNP.} External databases and user-provided data are used as input. Output of data is done using the website, the \emph{Distributed Annotation System} and a JSON-API.} 
	\label{Figure4_label}
\end{figure}

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp E. Bayer$^{2}$, 
Helge Rausch$^{3}$,
Fabian Zimmer$^{4}$,
Julia Reda$^{5}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} Applied Bioinformatics Group, School of Agriculture and Food Sciences, The University of Queensland, Australia
\\
\bf{3} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{4} Evolutionary Genomics and Transcriptomics Lab, Department of Genetics, Evolution and Environment, University College London, England
\\
\bf{5} Johannes Gutenberg University Mayence, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.5]{25_10_2012_Graphs/papers_dotchart.png}
	\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Flow of data inside openSNP.} External databases and user-provided data are used as input. Output of data is done using the website, the \emph{Distributed Annotation System} and a JSON-API.} 
	\label{Figure4_label}
\end{figure}
